Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-24 cbm-rbd-paper.tex
work on policy section intro

We can now derive the adaptive / dynamic maintenance policy
that resembles a CBM policy.
However, instead of a determining a threshold for a degradation signal like in usual CBM policies,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease,
and whenever $\tausnow$ decreases below $\tsetup$, the timespan needed to set up maintenance work
(often referred to as setup time),
a preventive maintenance action is initiated.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
using the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
Each operational cycle starts with the system being in an (as good as) new state,
i.e., all components in the system are new and have not aged.
A cycle ends when the system is either maintained preventively at $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.
We assume that either maintenance action takes negligible time,
and that either action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle begins under identical conditions.

***info from finished cycle is added to component knowledge base,
thus included in $\nkz$ and $\ykz$ for the following cycle.

Therefore, at each present time $\tnow$
(at a frequency small enough to be negligible on the system lifetime scale),
the current residual life distribution $\Rsysnow(t)$ is recalculated,
and the corresponding $\tausnow$ determined.

***as $\Rsysnow(t)$ on discrete grid until horizon, optimize $\tausnow$ over same discrete grid.
if $\gnow(\tau)$ always decreasing, corrective maintenance strategy! so we can switch maintenance policy!

@@

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \Tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite.

$\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient (****)

@@

\subsection{Operational procedure}

*** could update $\tau_*$ every time a component fails,
but (near) real-time update of $\tau_*$ possible and useful as non-failed components still contribute to knowledge base via right-censored observation $\tpnow$.

>>>>

We can now derive the adaptive / dynamic maintenance policy
that resembles a CBM policy.
However, instead of determining a threshold for a degradation signal like in usual CBM policies,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
Let $\tsetup$ be the timespan needed to set up maintenance work,
often referred to simply as setup time.
As soon as $\tausnow$ decreases below $\tsetup$,
a preventive maintenance action is initiated.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.

Each operational cycle starts with the system being in an (as good as) new state,
i.e., all components in the system are new and have not aged.
A cycle ends when the system is either maintained preventively at time $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.
The calculation of $\tausnow$ thus resembles the calculation
of the maintenance interval in an age based policy.
However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
our policy is adaptive and dynamic like a CBM policy.

It is possible that $\gnow(\tau)$ is monotonely decreasing, corrective maintenance strategy! so we can switch maintenance policy!

During a cycle,
$\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
This is possible because we use a fast discrete approximation of the unit cost rate function.

***as $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.

*** could update $\tausnow$ every time a component fails,
but (near) real-time update of $\tau_*$ possible and useful,
as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the lifetimes and censoring observed during the previous cycle.
We assume that both planned and unplanned maintenance action takes negligible time,
and that either action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.

@@

To determine the optimal time to maintenance $\tausnow$,

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \Tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}

***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite because of $1/t$.
we have no problem because of discrete approximation of $\Rsysnow(t)$ resp. $\fsysnow(t)$.
($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)

@@
